Syntax and Semantics of Abstract Binding Trees

### 2015-11-12 paper.tex
[paper] fix typo

Variables are interpreted by the map
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x:\tau}_P$ which
projects them from the environment and embeds them into the model. Metavariables
are resolved by the map
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash\MApp{\MV{m}}{\vec{u}}{\vec{M}}
  : \tau}_P$ (where
$\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}}$) which
projects their interpretation from the environment and intantiates it via
substitution:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{P_\tau}}
    \&[8.0em] {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
      \arrow[rr, dashed, "\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x:\tau}_P"]
      \ar{drr}[
        , rotate = -16.5
        , xshift = +1.5em
        , yshift = -0.2em
        , swap
      ]{{\nu}_{\Gamma} {\pi}_{3}}
      \ar{dl}[
        , rotate = +11.5
        , xshift = -2.75em
      ]{\IMode{\Tuple{\pi_\MV{m}\,\pi_1, \phi\,\pi_2, \psi}}}
      \arrow[l, dashed, swap, "\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash\MApp{\MV{m}}{\vec{u}}{\vec{M}}: \tau}_P"]
    \&[-2.0em]
    \&[+3.0em]{\IMode{P_\tau}}
    \\
    {\IMode{P_{\tau}^{\Yoneda{\vec{\sigma}\parallel\vec{\tau}}}\times S^{\{\vec{\sigma}\}} \times P^{[\vec{\tau}]}}}
      \arrow[u, "\IMode{\varsigma^\tau_{\vec{\sigma}\parallel\vec{\tau}}}"]
    \&{}
    \&{}
    \& {\IMode{P^{[\Gamma]}}}
      \arrow[u, swap, "{\pi}_{x}"]
    \\
    {\IMode{P^{[\vec{\tau}]}}}
    \& {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
      \arrow[l, swap, "\Define{\psi\,}{\,\Tuple{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M:\tau}_P}_{(M,\tau)\in (\vec{M},\vec{\tau})}}"]
    \& {\IMode{S^{\{\Upsilon\}}}}
      \arrow[r, "\Define{\phi\,}{\,\Tuple{\pi_u}_{u\in\vec{u}}}"]
    \& {\IMode{S^{\{\vec{\sigma}\}}}}
  \end{tikzcd}
\]

>>>>

Variables are interpreted by the map
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x:\tau}_P$ which
projects them from the environment and embeds them into the model. Metavariables
are resolved by the map
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash\MApp{\MV{m}}{\vec{u}}{\vec{M}}
  : \tau}_P$ (where
$\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}}$) which
projects their interpretation from the environment and instantiates it via
substitution:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{P_\tau}}
    \&[8.0em] {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
      \arrow[rr, dashed, "\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x:\tau}_P"]
      \ar{drr}[
        , rotate = -16.5
        , xshift = +1.5em
        , yshift = -0.2em
        , swap
      ]{{\nu}_{\Gamma} {\pi}_{3}}
      \ar{dl}[
        , rotate = +11.5
        , xshift = -2.75em
      ]{\IMode{\Tuple{\pi_\MV{m}\,\pi_1, \phi\,\pi_2, \psi}}}
      \arrow[l, dashed, swap, "\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash\MApp{\MV{m}}{\vec{u}}{\vec{M}}: \tau}_P"]
    \&[-2.0em]
    \&[+3.0em]{\IMode{P_\tau}}
    \\
    {\IMode{P_{\tau}^{\Yoneda{\vec{\sigma}\parallel\vec{\tau}}}\times S^{\{\vec{\sigma}\}} \times P^{[\vec{\tau}]}}}
      \arrow[u, "\IMode{\varsigma^\tau_{\vec{\sigma}\parallel\vec{\tau}}}"]
    \&{}
    \&{}
    \& {\IMode{P^{[\Gamma]}}}
      \arrow[u, swap, "{\pi}_{x}"]
    \\
    {\IMode{P^{[\vec{\tau}]}}}
    \& {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
      \arrow[l, swap, "\Define{\psi\,}{\,\Tuple{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M:\tau}_P}_{(M,\tau)\in (\vec{M},\vec{\tau})}}"]
    \& {\IMode{S^{\{\Upsilon\}}}}
      \arrow[r, "\Define{\phi\,}{\,\Tuple{\pi_u}_{u\in\vec{u}}}"]
    \& {\IMode{S^{\{\vec{\sigma}\}}}}
  \end{tikzcd}
\]
